---
title: "Lab-webscraping"
author: "Lin Pin Tzu (Ruby)"
date: '2022-07-07'
output:
  pdf_document: default
  html_document: default
---

```{r,include=FALSE}
library(rvest)
library(tidyverse)
library(dplyr)
```

# 3) Using the web address "https://en.wikipedia.org/wiki/ITF_Rankings" and the R coding structure presented in class to web scrape the following table found on the page.
```{r}
wikiurl <- read_html(
  "https://en.wikipedia.org/wiki/ITF_Rankings")
datatables <- wikiurl%>%
  html_table(., fill = T)
datatables[[3]] -> dt 
dt
```

# 4) Using the web address "https://www.mlb.com/stats/2018"  and the R coding structure presented in class, web scrape the table found on the page.
```{r}
wikiurl1 <- read_html("https://www.mlb.com/stats/2018")
baseballdata2018 <- wikiurl1%>%
  html_table(., fill = T) 
baseballdata2018[[1]] -> BD2018 
BD2018
```

# 5) Use and show R code to find the average number of hits for all players in the table from number 4
```{r}
mean(BD2018$HH)
```

# 6) Use and show R code to produce a boxplot for the number of hits (use tidyverse/ggplot coding). Use the data table from number 4
```{r}
boxplot(BD2018$HH)
#ggplot
ggplot(data=BD2018,mapping = aes(x=HH))+
  geom_boxplot(fill="light blue")+
  ggtitle("Number of hits")+
  theme_bw()
```

# 7) Use and show dplyr coding to determine which player had the greatest number of strikeouts using the data table from number 4.
```{r}
BD2018 %>%
  select(PLAYERPLAYER,SOSO) %>%
  arrange(desc(SOSO)) %>%
  slice(1)
```

# 8) Use and show dplyr coding to show the batting averages for Washington Nationals players and Colorado Rockies players using the data table from number 4
```{r}
BD2018 %>%
  filter(TEAMTEAM =="WSH"|TEAMTEAM =="COL") %>%
  select(TEAMTEAM,AVGAVG) %>%
  group_by(TEAMTEAM)
```