---
title: "Lab2"
author: "Lin Pin Tzu (Ruby)"
date: '2022-06-30'
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
```

```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
V
str(V)
```

# 1) Why is the vector shown above an atomic vector? (Explain using two or three sentences)
Atomic vector show logical, integer , numeric , complex , character, or raw and can have any attributes except a dimension attribute, and atomic vector only shows the same type of object.

# 2) Use and show R code that will extract "Dolphins" from the vector shown above.
```{r}
V[3]
```
# 3) Use and show Rcode that will extract "Bears" , "Dolphins" and "Bengals" from the vector shown above.
```{r}
V[c(1,3,5)]
```
# 4) Use and show two Rcoding methods that will show all objects of the vector given above except "Bears". 
```{r}
V[-1]
V[2:5]
```

## K <- list( x = 3:7, "never", 43, y = list(10,20,30))
# 5) Why is the vector given above called a list? (Explain in two or three sentences) If the vector is a list, identify the type of each object in the list.

List shows logical, integer , numeric , complex , character, or raw and can have any attributes except a dimension attribute but list can show different types of objects.

```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
str(K)
```
# 6) Use and show R code that will give the length of the vector shown above.
```{r}
length(K)
```
# 7) Use and show R code that will output the fourth object in the vector shown above.
```{r}
K[4]
```
# 8) Use and show R code that will show all objects in the vector (list) given above.
```{r}
K[]
str(K)
```
# 9) Copy paste and run the tribble given below.
```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt

dt
```
# 9a) Use and show a map function to find the mean of each column of the dt data table
```{r}
map_dbl(dt,mean)
```
# 9b) Use and show a map function to find the standard deviation of each column of the dt data table.
```{r}
map_dbl(dt,sd)
```
# 9c) Use and show a map function that will calculate the square root of each value of each column of the data table dt.
```{r}
dt %>%
  map(~.^(.5)) -> d 
d

sqrt(dt)
```
# 9d) Use R code to find the mean, max, 1st Quartile, 2nd Quartile,Median, and Mean for each column of the dt data table. (Hint: You do not have to use a map function)
```{r}
summary(dt)
```
