---
title: "lab3"
author: "Lin Pin Tzu (Ruby)"
date: '2022-07-05'
output:
  pdf_document: default
  html_document: default
---

```{r,include=FALSE}
library(tidyverse)
library(dplyr)
library(purrr)
```

# 1) For the lists given above, show and use R code (a map function) to iteratively find the square of the sums across the vectors
```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)
```

```{r}
pmap_dbl(list(x,y,z),sum)^2
```


```{r}
tribble( ~Student,  ~Gender,    ~Salary,
           "John",   "Male",       65000,
           "Alice",  "Female",    73000,
            "Juan",   "Male",       66000,
             "Beth",  "Female",    71500,
             "Denise", "Female",  82000
) -> table
table
```
# 2) Using the data table above, use and show R code that will output a statement thatis descriptive for all rows of the data table.The first row is given below.  Your code should produce the other specific statements. John who is Male, has a salary that is 65000 dollars per year.
```{r}
table %>% 
  pmap_chr(~ str_glue("{..1} who is {..2}, has a salary that is {..3} dollars per year ")) 
```

# 3) Write a nested loop that will produce a 5 by 5 matrix that whose matrix elementsare sums of the corresponding columns and rows.Your code should produce the matrix below:
```{r}
z <- matrix( nrow = 5, ncol = 5)
for (m in 1:5) {
  for (n in 1:5) {
    z[m, n] <- (m + n)
  }
}
print(z)

```
# 4) Use for loop coding to produce the number sequence shown below: Note that the numbers 5 and 10 are missing
```{r}
x <- 1:20 
for (val in x) {
  if (val == 5)
    next
    if (val == 10)
    next
  print(val)
}
```
